Modeling the impacts of replacing car trips with combined public transport and cycling: \ Reproducible methods, results and actionable evidence from biclaR

### 2024-04-18 paper/PaperCEUS/PaperCEUS_rev1.Rmd
Update with tracked changes code
jitter fig 2

@@

Combining public transportation (PT) and cycling for the first and last mile in metropolitan areas can replace a high proportion of private car trips [@MARTENS2007326].
In The Netherlands, which has the highest mode share of cycling in the world, cycling accounts for more than a third of all trips to and from rail stations at the 'home' end of the journey, greatly increasing the ability of the transport system [@RIETVELD200071].
This approach to reducing car dependency and associated externalities requires interventions and programs to make bicycling more appealing [@lapaix_role_2021].
The resulting public investments can have significant social and environmental benefits [@internationaltransportforum_integrating_2017].
Despite the benefits of cycling-PT intermodality, the potential of this combination is often overlooked in transport planning [@lapaix_role_2021].
<!-- Many studies refer to the potential of cycling and bike-sharing to replace car and PT trips, but not to the potential of serving as first and last miles. -->

@@

```{r jitter, fig.align='center', fig.cap="Representation of desire lines in the Lisbon metropolitan area between districts, without jittering (left) and with jittering (right).", out.width="100%"}

# od_all = readRDS("paper/paperTRA/load/od_all.Rds")
# od_jittered_filter = readRDS("paper/paperTRA/load/od_jittered_filter.Rds")
# 
# par(mfrow = c(1, 2))
# plot(od_all$geometry, lwd = 0.1)
# plot(od_jittered_filter$geometry, lwd = 0.1)

knitr::include_graphics("img/jitter.png", error = FALSE)

>>>>

```{r eval=FALSE, echo=FALSE}
system("latexdiff paper/PaperCEUS.tex paper/PaperCEUS_rev1.tex > paper/PaperCEUS_diff.tex")

@@

Combining public transportation (PT) and cycling for the first and last mile in metropolitan areas can replace a high proportion of private car trips [@MARTENS2007326].

test

In The Netherlands, which has the highest mode share of cycling in the world, cycling accounts for more than a third of all trips to and from rail stations at the 'home' end of the journey, greatly increasing the ability of the transport system [@RIETVELD200071].
This approach to reducing car dependency and associated externalities requires interventions and programs to make bicycling more appealing [@lapaix_role_2021].
The resulting public investments can have significant social and environmental benefits [@internationaltransportforum_integrating_2017].
Despite the benefits of cycling-PT intermodality, the potential of this combination is often overlooked in transport planning [@lapaix_role_2021].
<!-- Many studies refer to the potential of cycling and bike-sharing to replace car and PT trips, but not to the potential of serving as first and last miles. -->

@@

```{r jitter, fig.align='center', fig.cap="Representation of a flow-weighted random sample of 10,000 desire lines in the Lisbon metropolitan area between districts, without jittering (left) and with jittering (right).", out.width="100%"}

# od_all = readRDS("paper/paperTRA/load/od_all.Rds")
# od_jittered_filter = readRDS("paper/paperTRA/load/od_jittered_filter.Rds")
# 
# par(mfrow = c(1, 2))
# plot(od_all$geometry, lwd = 0.1,)
# plot(od_jittered_filter$geometry, lwd = 0.1)
# knitr::include_graphics("img/jitter.png", error = FALSE)
# 
# 
# odcombined = rbind(
#   od_all |> 
#     transmute(Total, Disaggregation = " Original"),
#   od_jittered_filter |> 
#     transmute(Total, Disaggregation = "Jittered")
# )
# odcombined |> 
#   sample_n(10000, weight = odcombined$Total) |>
#   mutate(Total = Total / 1000) |> 
#   ggplot() +
#   geom_sf(aes(alpha = Total)) +
#   facet_wrap(~Disaggregation) +
#   theme_void() +
#   geom_sf(data = MUNICIPIOSgeo, fill = NA, color = "gray60")

knitr::include_graphics("img/jitter_rev.png", error = FALSE)
```
